An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-03-04 docs/icccn2009/paper.tex
Some text on DSP
git-svn-id: svn://localhost/netbeams/trunk@331 559edde2-a4d4-44e0-96fc-4035e40d7396

\section{DSP}

@@

\subsection{Data Sensor Framework and Platform}

should include a picture of a standalone DSP showing a DC and a DP
(general description only). Explain difference between DSP Framework
and DSP Platform. This section should give a top-level overview.
Subsequent sub-sections should explain certain features of the DSP in
more detail.

@@

\subsection{DP and DC}

@@

\subsection{DSP Message}

>>>>

\section{Data Sensor Platform}

@@

\subsection{Architecture}

Our architecture is based on a micro-kernel approach. The core
functionality is limited to a minimum and all extra services are built
as plug-and-play modules on top of the micro-kernel. With the help of
this approach we can keep the basic infrastructure compact while
allowing customization via special-purpose modules. In our terminology
we call the basic foundation the \emph{Data Sensor Platform}
(DSP). The scope of the DSP is one address space of an execution
platform. A sensor network is built from several DSPs that are linked
with each other.

Figure \ref{FIG_DSP} depicts the basic architecture of the
DSP. We refer to the plug-and-play modules as DSP Components. DSP
Components are self-contained modules that can be added and removed to
a DSP installation at runtime. The basic communication paradigm within
a DSP is a message. DSP Components can exchange messages of different
types. We distinguish between Data Producers (DP) and Data Consumers
(DP) within the scope of a DSP. DP and DC can be seen as roles that a
DSP Component may have. It is possible for a DSP Component to act in
the role of DC and DP at the same time.

@@

The DSP is responsible for routing messages between DPs and DCs. It is
important to note that this routing only happens withing a
DSP. Following the paradigm of a micro-kernel approach, the DSP has no
notion of remote communication or sensor-specific details. All this
knowledge is embodied in DSP Components.

\subsection{Components}

@@

\begin{code}
interface DSPComponent
{
   public String getComponentType();
   public void initComponent(...);
   public void startComponent();
   public void stopComponent();
   public void deliver(DSPMessage msg);
   public Message deliverWithReply(DSPMessage msg);
   // ...
}
\end{code}

\subsection{Message}
